R Notebook

### 2020-09-10 R/ICCHP20.Rmd
Update dep management

if (!require(knitr)) install.packages("knitr")
if (!require(pacman)) install.packages("pacman")
pkg_list <- c("tidyverse", "glue", "magrittr", "plotly", "moments", "emmeans", "conflicted", "gridExtra", "kableExtra", "rcompanion", "broom", "rstatix", "ggpubr", "Rmisc")

pacman::p_load(char = pkg_list) #update=TRUE

knitr::opts_chunk$set(
  warning = FALSE,
  echo = FALSE,
  message = FALSE,
  error=FALSE,
  cache = FALSE
)

options(scipen=999, digits=4)

@@

initial.data <- "../data/initial.csv"

conflict_prefer("arrange", "plyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("summarize", "dplyr")
conflict_prefer("layout", "plotly")

@@

```{r results='hide'}
data.wide <- read_csv(initial.data) %>% 
  select(-X1) %>% 
  mutate(mode = ifelse(mode == "N", "NG", "G")) %>%
  rename("Condition" = mode, "Hotspot" = hotspot) %>%
  mutate(across(c(Hotspot, Condition), as.factor)) %T>% print

data.long <- data.wide %>%
  mutate(id = seq_along(Hotspot), .before = Hotspot) %>%
  pivot_longer(cols = "P1":"P4", names_to="Participant", names_transform = list(Participant = as.factor), values_to = "Time") %>%
  relocate(Participant, id, Condition, Hotspot, Time) %>%
  #mutate(Hotspot = factor(Hotspot, levels = hs.order)) %>%
  dplyr::arrange(Participant, id) %T>% print
```
***
# Wilcoxon
***

@@

>>>>

source("../utils/dependencies.R", echo=F)

pkg_list <-
  c("knitr",
    "tidyverse",
    "dplyr",
    "glue",
    "magrittr",
    "plotly",
    "moments",
    "emmeans",
    "conflicted",
    "gridExtra",
    "kableExtra",
    "rcompanion",
    "broom",
    "broom.mixed",
    "afex",
    "ggpubr",
    "Rmisc",
    "lme4",
    "survival",
    "coxme",
    "survminer",
    "easystats/see",
    "easystats/report",
    "easystats/performance",
    "stargazer",
    "jtools",
    "gtools"
  )

update_packages(pkg_list)

options(install.packages.check.source = "no", scipen=999, digits=4)

knitr::opts_chunk$set(
  warning = TRUE,
  echo = FALSE,
  message = TRUE,
  error = TRUE,
  cache = FALSE
)

@@

conflict_prefer("arrange", "plyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("summarize", "dplyr")
conflict_prefer("layout", "plotly")
conflict_prefer("here", "here")

initial.data <- here("data", "initial.csv")

@@

```{r results='hide'}
data.wide <- read_csv(initial.data) %>% 
  select(-X1) %>% 
  mutate(mode = ifelse(mode == "N", "NG", "G")) %>%
  rename("Condition" = mode, "Hotspot" = hotspot) %>%
  mutate(across(c(Hotspot, Condition), as.factor)) #%T>% print

data.long <- data.wide %>%
  mutate(id = seq_along(Hotspot), .before = Hotspot) %>%
  pivot_longer(cols = "P1":"P4", names_to="Participant", names_transform = list(Participant = as.factor), values_to = "Time") %>% 
  mutate(Success = as.integer(ifelse(Time >= 120, 0, 1))) %>%
  relocate(Participant, id, Condition, Hotspot, Success, Time) %>%
  #mutate(Hotspot = factor(Hotspot, levels = hs.order)) %>%
  dplyr::arrange(Participant, id)  %T>% print
```

***
# Wilcoxon
***

@@

<!--------------------------------------------------------------------------------->
<!--------------------------------------------------------------------------------->

## Analysis tests:
***

### Model building:

```{r}
cox.mod <- coxph(Surv(Time, Success) ~ Condition + frailty.gaussian(Participant) + frailty.gaussian(Hotspot), data = data.long)
cox.mod.min <- coxph(Surv(Time, Success) ~ 1 + frailty.gaussian(Participant) + frailty.gaussian(Hotspot), data = data.long)
summary(cox.mod)
```

```{r}
model_performance(cox.mod)
```

```{r}
anova(cox.mod, cox.mod.min)
```

### With cox.me:

```{r}
cox_me <- coxme(Surv(Time, Success) ~ Condition + (1 | Participant) + (1 | Hotspot), data = data.long)
cox_me.min <- coxme(Surv(Time, Success) ~ 1 + (1 | Participant) + (1 | Hotspot), data = data.long)
summary(cox.me)
```

```{r}
AIC(cox.me)
```

```{r}
anova(cox_me, cox_me.min)
```

### Model evaluation:

```{r}
# ggcoxzph(cox.zph(cox.mod))
```

```{r}
ggcoxdiagnostics(cox.mod,
 type = "schoenfeld",
 ox.scale = "linear.predictions")
```

```{r}
ggforest(cox.mod)
```
